This thesis represents the culmination of my, by now, nearly ten-year-long fascination with variable stars, which began way back in my first year of university. 
It would have been all but impossible to chase this dream without the support of many individuals. 
I would like now to give thanks to all those who have supported me on this journey. 

I would first like to thank my doctoral advisors, Dr.\ ir.\ Saskia Hekker and Prof.\ Dr.\ Sarbani Basu, for their advice, guidance, and good ideas over the past three years. 
I appreciate the amount they pushed me to make this thesis what it is, and I look back with amazement at all the things I have been given the opportunity to learn about. 
I am proud of the hard work that they encouraged from me, and I look forward to continued collaboration in the future. 

During my studies, I have had the great fortune of being able to lean on the expertise of two post-docs, Dr.\ George Angelou and Dr.\ Warrick Ball. 
Without their help, I would have surely been stuck in the dark for far longer than I was. 
I want to especially thank George for teaching me about stellar evolution, and to thank Warrick for teaching me about kernels. 
I hope we will continue to collaborate long into the future! 

Next I want to thank the SAGE Group at the Max Planck Institute for Solar System Research and the Department of Astronomy at Yale University for hosting me over these three years. 
I have greatly enjoyed my stays, the exchange of ideas, and the numerous friendships that I've made in these places. 
I want to specifically thank Dr.\ Andr\'es Garc\'ia Saravia Ortiz de Montellano and Dr.\ Timo Reinhold for their valued help with this thesis. 
I also thank the IMPRS scientific coordinator, Dr.\ Sonja Schuh, and the staff at both Yale University and the MPS for all their assistance. 
I especially want to thank the IMPRS Student Group, which makes it easy for anyone from anywhere to fit in and make friends. 
%

Special thanks go to the Director of the Max Planck Institute for Solar System Research, Prof.\ Dr.\ Laurent Gizon; the Director of the GWDG, Prof.\ Dr.\ Ramin Yahyapour; and the Dean of Computer Science, Prof.\ Dr.\ Jens Grabowski for helping me to enroll into the 
%
%
G\"ottingen Ph.D.\ Programme in Computer Science. 
Additionally, I thank the remaining members of the examination board, Prof.\ Dr.\ Carsten Damm, Jun.\ Prof.\ Dr.\ Ing.\ Marcus Baum, and Prof.\ Dr.\ Yvonne Elsworth, FRS for agreeing to examine this thesis. 

I thank the National Physical Science Consortium for their very generous support in the form of a graduate fellowship over five years of my graduate studies. 
I also thank Dr.\ Judith E.\ Devaney Terrill for selecting me for the NPSC Fellowship, for hosting me at NIST for two summers, and especially for always encouraging a strong scientific mindset. 

I have had the privilege and honor of working with and (co-)supervising several wonderful students over the course of my graduate studies. 
I want to acknowledge: Felix Ahlborn (now a Ph.D.\ student at the Max Planck Institute for Astrophysics), Kenny Roffo (now employed at the NASA Jet Propulsion Laboratory and pursuing graduate studies at Johns Hopkins University), Marc Hon (finishing up his Ph.D.\ at the University of New South Wales in Sydney, Australia), and Alejandra Perea Rojas (in the midsts of applying to prestigious universities). 
I'm proud of you all - keep up the great work! 

At the Max Planck Institute for Solar System Research, we started a band called MegaGau{\ss} that practices every Monday evening and provides a much needed reprieve from the sometimes rollarcoaster-like nature of academia. 
I want to thank everyone who has played and participated over the last three years and over the many gigs we had; this list includes over twenty people! 
With no guarantee of completeness, the band included 
Abbey Ingram, %
Alessandro Cilla, %
Bastian Proxauf, %
Carla Wiles, %
ChiJu Wu, %
Daniel Maase,
David Marshall, %
Fatima Kahil, %
Felix Mackebrandt, %
Hans Huybrighs, %
Holly Waller, %
Katja Karmrodt, %
Kenny Roffo, %
Nils Gottschling, %
Robin Thor, %
Sudharshan Saranathan, %
Dr.\ Ankit Barik, %
Dr.\ David Martin Belda, %
Dr.\ Emanuele Papini, %
Dr.\ James Kuszlewicz, %
Dr.\ Keaton Bell, %
Dr.\ Theodosis Chatzistergos, and
Dr.\ Vera Dobos. %
Special thanks go out to my ``other half'' of the rhythm section, Helge Mi{\ss}bach, without whom there would have been no band! 

I want to take this opportunity to thank some of the teachers who have encouraged and inspired me over the years. 
This list includes my high school English, history, and physics teachers: Mr.\ Nelson, Mr.\ Kaufman, Mr.\ Battisti; and several of my college computer science professors: Prof.\ Vampola, Prof.\ Graci, and Prof.\ Dr.\ Early. 

To my `cohort' in the IMPRS school, Alessandro Cilla and Fatima Kahil, and to my other graduate student friends as well: best of luck with finishing your studies! 
To my friend K.\ Casey Shea, thank you for making this amazing thesis cover design for me! 
To all of my dear friends whom I have made over these years of study, thank you for making this journey more enjoyable than it certainly could have been. 
%
%
%
%
%
%
%
Special thanks go to Carla Wiles, for many things, including her support and her valued opinions on all the aesthetic aspects of this thesis. 

I want to thank my family for their unwavering support in my choice to study something as academic as the distant stars. 
I thank my mother Patricia, my father Paul, my sister Bobbie Lee, her partner Johnny, my brother Sean, my sister-in-law Valentina, my niece Nia, my nephews Rashay and Darius, and my step-parents Ron and Nina. 

Last, and certainly not least, I dedicate this thesis to my mentor, Prof.\ Dr.\ Shashi M.\ Kanbur, who has continuously and actively encouraged me over the past decade to pursue my ``academic dreams.'' 
Thank you, Shashi, for always being there for me, and for showing me the light of variable stars. 
